---
title: "Methodology"
format: html
freeze: auto
---
```{r}
#| warning: false
#| message: false
#| label: load packages and authenticate
#| include: false
# Load required packages
library(dplyr)
library(bggUtils)
library(tidymodels)
library(vetiver)
library(targets)
library(qs2)
library(reactable)
library(fs)

# Load source code
tar_source("src")

# Project settings
config <- config::get()

# Authenticate to GCS
authenticate_to_gcs()

# set ggplot theme
theme_set(bggUtils::theme_bgg())
```


```{r}
#| warning: false
#| message: false
#| include: false
#| label: load artifacts

# Load objects from pipeline
tar_load(hurdle_threshold)
tar_load(valid_predictions)
tar_load(valid_metrics)
tar_load(details)
tar_load(hurdle_threshold)
tar_load(valid_hurdle_metrics)
tar_load(hurdle_results)

# find valid_years
valid_years =
    valid_predictions |>
    summarize(min_year = min(yearpublished), max_year = max(yearpublished))

```

```{r}
#| include: false
#| label: load games from gcs

# load games from gcp
games =
    get_games_from_gcp(bucket = "bgg_data")

# prepare games with preprocessor
active_games =
    games |>
    prepare_games()
```

```{r}
#| warning: false
#| message: false
#| label: load models
#| include: false
# Create model board connection
model_board <- gcs_model_board(bucket = config$bucket, prefix = config$board)

# Load model metadata
tar_load(averageweight_vetiver)
tar_load(average_vetiver)
tar_load(usersrated_vetiver)
tar_load(hurdle_vetiver)

# load models
averageweight_fit <- pin_read_model(model_board, averageweight_vetiver)
average_fit <- pin_read_model(model_board, average_vetiver)
usersrated_fit <- pin_read_model(model_board, usersrated_vetiver)
hurdle_fit <- pin_read_model(model_board, hurdle_vetiver)
```

# About

The goal of this project was to train models to predict new and upcoming releases once information about them becomes available on BoardGameGeek. How do you train a model to predict new releases?

I use historical data from BoardGameGeek (BGG) to train a number of predictive models for community ratings. I train a series of models for this purpose.

- I first classify games based on their probability of achieving a minimum number of ratings on BGG. 
- I then estimate each game's complexity (average weight) in order to predicts its number of user ratings and average rating. 
- I then use these estimates to predict the expected Geek Rating.

## Methodology

I develop and train models using a training-validation approach based around the year in which games were published. I create a training set of games published prior to **`r valid_years$min_year`** and evaluated its performance in predicting games published from **`r valid_years$min_year`** to **`r valid_years$max_year`**.

```{mermaid}
graph LR
    %% Data Sources and Storage
    BGG[BoardGameGeek API] -->|Data Collection| GCS[(Google Cloud Storage)]
    GCS -->|Data Loading| PrepData[Preprocessed Games Data]
    
    %% Data Splitting
    PrepData -->|Time-based Split| DataSets[Training/Validation/Testing Sets]
    
    %% Main Model Components
    DataSets -->|Training| Models[Model Training]
    
    %% Model Types
    Models --> HurdleModel[Hurdle Model<br>Classification]
    Models --> WeightModel[Complexity Model<br>Regression]
    Models --> RatingModels[Rating Models<br>Regression]
    
    %% Evaluation and Deployment
    HurdleModel --> Evaluation[Model Evaluation]
    WeightModel --> Evaluation
    RatingModels --> Evaluation
    
    Evaluation --> Tracking[Performance Tracking]
    Evaluation --> Deployment[Model Deployment]
    
    %% Styling
    classDef storage fill:#f9f,stroke:#333,stroke-width:2px;
    classDef model fill:#bbf,stroke:#333,stroke-width:1px;
    classDef data fill:#dfd,stroke:#333,stroke-width:1px;
    
    class GCS,VetiverModels storage;
    class HurdleModel,WeightModel,RatingModels,Models model;
    class PrepData,DataSets,NewGames,Predictions data;
```

## Data

```{r}

# data
# raw pull from bgg
tar_load(games_raw)
# split for train/valid/test
tar_load(split)

# get training set
train_data =
    split |>
    training()

# get validation set
valid_data =
    split |>
    validation()

# full data
full_data =
    bind_rows(train_data, valid_data)
```

# Data

As of my most recent data job, there are **`r nrow(games)`** individual games on BGG. For each of these games, I have information about the game (playing time, mechanisms, components, publishers, artists, designers, etc), as well as information voted on by the BGG community (average rating, average weight).

```{r}

full_data |>
    sample_n(1000) |>
    visdat::vis_dat()

```

## Outcomes

The data is at the game level, where I observe the BGG community’s aggregated ratings for individual games. This means I do not have data on the underlying ratings for games, only the average, standard deviation, or sum of the distribution.

I examine four different community outcomes for games: average weight rating (complexity), number of user ratings, average user rating, and geek rating. Only a subset of games have received enough votes by the BGG community to receive a geek rating, which is a bayesian average based on the number of ratings as well as the average rating. 

```{r}
#| message: false

full_data |>
    filter_geek() |>
    log_ratings() |>
    plot_outcomes_distributions() +
    theme_set(theme_light() + theme(legend.position = 'top'))

```

Each of these BGG outcomes (average weight, average, user ratings) is related to each other in some way, which is important to keep in mind as we think about modeling these outcomes. 

The average weight tends to be highly correlated with the average rating, while not being correlated with the number of user ratings. The geek rating is a function of the average and user ratings, which means it is also then correlated with the average weight.

```{r}

full_data |>
    plot_outcomes_relationships() +
    theme_set(theme_light() + theme(legend.position = 'top'))

```

### Number of Ratings

I train and evaluate the models primarily on games that have achieved at least 25 ratings, as this is the required number of user ratings for a game to receive a Geek rating. 

The majority of games on BoardGameGeek do not actually receive this number of ratings, especially in recent years as the number of games published has dramatically increased. My main aim is to predict games that are set to be published and available to purchase, and many of the over 100k games on BGG have not been been published or distributed. 

Ideally, I would have a variable that measures this directly, but I instead rely on achieving a minimum number of ratings as a heuristic.

```{r}

plot_games_by_split = function(data) {
    plot_data =
        data |>
        bggUtils:::unnest_outcomes() |>
        inner_join(
            data |>
                bggUtils:::unnest_info()
        ) |>
        add_hurdle() |>
        mutate(
            yearpublished = case_when(
                yearpublished < 1950 ~ 1949,
                TRUE ~ yearpublished
            )
        ) |>
        mutate(
            hurdle = case_when(
                hurdle == 'yes' ~ '>25 ratings',
                hurdle == 'no' ~ '<25 ratings'
            )
        ) |>
        group_by(yearpublished, hurdle) |>
        count()

    plot_data |>
        ggplot(aes(x = yearpublished, y = n, fill = hurdle)) +
        geom_col() +
        scale_color_manual(values = c("grey60", "navy"))
}

plot_games_by_split(games) +
    scale_fill_manual(values = c('coral', 'navy'))

```

In predicting new games, I first use a hurdle model to predict whether games are expected to receive enough ratings to be assigned a Geek rating (25 ratings). This model is trained on the full universe of games, whereas the others are trained on games with at least 25 ratings.

The model for predicting the average weight is trained on games that have received 25 ratings and have also received at least 5 votes on their complexity.

```{r}

bind_rows(
    as_tibble(hurdle_fit$metadata$user$data) |>
        group_by(model = 'hurdle') |>
        count(),
    as_tibble(average_fit$metadata$user$data) |>
        group_by(model = 'average') |>
        count(),
    as_tibble(averageweight_fit$metadata$user$data) |>
        group_by(model = 'averageweight') |>
        count(),
    as_tibble(usersrated_fit$metadata$user$data) |>
        group_by(model = 'usersrated') |>
        count()
) |>
    ungroup() |>
    rename(games = n) |>
    arrange(desc(games)) |>
    gt::gt()

```


## Assessment

How did the models perform in predicting games? I evaluated the model on games published in `r valid_years$min_year` and `r valid_years$max_year`.

```{r}

valid_predictions |>
    group_by(yearpublished) |>
    count() |>
    ungroup() |>
    gt::gt()

```

### Hurdle

I first used the hurdle model to classify whether games would receive at least 25 ratings.

I set the probability threshold at `r hurdle_threshold` - this was the point that maximized the F2 score and minimized false negatives. For the purpose of the hurdle model, including a game that did not receive a Geek rating is much worse than missing a game that did. The main purpose of the model is filter out low-quality games.

::: {.panel-tabset}

#### Threshold

```{r}

valid_predictions |>
    ggplot(aes(x = .pred_hurdle_yes, fill = hurdle)) +
    geom_density(alpha = 0.5) +
    scale_color_manual() +
    theme(legend.title = element_text()) +
    xlab("Pr(User Ratings >= 25)") +
    scale_fill_manual(values = c("coral", "navy")) +
    guides(fill = guide_legend(title = 'User Ratings >=25')) +
    geom_vline(xintercept = hurdle_threshold, linetype = 'dashed')
```


#### Metrics

```{r}

prob_metrics = metric_set(yardstick::roc_auc, yardstick::pr_auc)

prob_hurdle_metrics =
    valid_predictions |>
    group_by(outcome = 'hurdle') |>
    prob_metrics(truth = hurdle, .pred_hurdle_yes, event_level = 'second')

valid_hurdle_metrics |>
    bind_rows(prob_hurdle_metrics) |>
    gt::gt() |>
    gt::tab_options(quarto.disable_processing = T) |>
    gt::fmt_number(columns = c(".estimate"), decimals = 3) |>
    gtExtras::gt_theme_espn()

```

#### Confusion Matrix

```{r}

valid_predictions |>
    conf_mat(hurdle, .pred_hurdle_class) |>
    autoplot(type = 'heatmap')

```

#### False Negatives

Which games that the model classified as "no" received 25+ ratings?

```{r}

valid_predictions |>
    filter(.pred_hurdle_class == 'no') |>
    filter(usersrated >= 25) |>
    select(yearpublished, game_id, name, usersrated, bayesaverage) |>
    arrange(desc(usersrated)) |>
    mutate(bayesaverage = round(bayesaverage, 3)) |>
    mutate(across(all_of(c("yearpublished", "game_id")), ~ as.factor(.x))) |>
    DT::datatable()

```

#### False Positives

Which games that the model classified as "yes" did not receive 25+ ratings?

```{r}

valid_predictions |>
    filter(.pred_hurdle_class == 'yes') |>
    filter(usersrated < 25) |>
    select(yearpublished, game_id, name, usersrated, .pred_bayesaverage) |>
    arrange(desc(usersrated)) |>
    mutate(.pred_bayesaverage = round(.pred_bayesaverage, 3)) |>
    mutate(across(all_of(c("yearpublished", "game_id")), ~ as.factor(.x))) |>
    DT::datatable()

```

:::

### Ratings

I evaluate predictions for the average weight rating, the average rating, the number of user ratings, and the Geek rating.

::: {.panel-tabset}

```{r}
#| message: false
#| warning: false
#| label: display plots for predictions from validation set

plot_data =
    valid_predictions |>
    pivot_outcomes() |>
    left_join(
        games |>
            bggUtils:::unnest_outcomes() |>
            select(game_id, usersrated),
        by = join_by(game_id)
    ) |>
    left_join(
        valid_predictions |>
            select(game_id, hurdle, .pred_hurdle_yes)
    ) |>
    mutate(
        hurdle = case_when(
            hurdle == 'yes' ~ '>25 ratings',
            hurdle == 'no' ~ '<25 ratings'
        )
    )

plot_hurdle_yes =
    plot_data |>
    filter(hurdle == '>25 ratings') |>
    plot_predictions(color = hurdle, alpha = 0.15) +
    scale_color_manual(values = c("navy")) +
    guides(color = 'none')

plot_hurdle_no =
    plot_data |>
    filter(hurdle == '<25 ratings') |>
    plot_predictions(color = hurdle, alpha = 0.15) +
    scale_color_manual(values = c("coral")) +
    guides(color = 'none')

```

#### Games with >25 Ratings

```{r}
#| warning: false
#| message: false
plot_hurdle_yes

```

#### Games with <25 Ratings

```{r}
#| warning: false
#| message: false
plot_hurdle_no

```

:::

```{r}

targets_tracking_details(metrics = valid_metrics, details = details) |>
    select(
        model,
        minratings,
        outcome,
        any_of(c("rmse", "mae", "mape", "rsq", "ccc"))
    ) |>
    filter(minratings == 25) |>
    select(minratings, everything()) |>
    gt::gt() |>
    gt::tab_options(quarto.disable_processing = T) |>
    gtExtras::gt_theme_espn()

```

What were the model's top predictions in the validation set?

```{r}
#| label: validation-predictions-table
#| column: page-inset-right

valid_predictions |>
    filter(.pred_hurdle_class == 'yes') |>
    select(-starts_with(".pred_hurdle")) |>
    slice_max(.pred_bayesaverage, n = 150, with_ties = F) |>
    predictions_dt(
        games = games,
        lazy_load = TRUE,
        pageLength = 10
    ) |>
    add_colors()

```

## Features

Which features were influential for predicting each BGG outcome?

```{r}
#| message: false
#| warning: false
average_plot =
    average_fit |>
    extract_vetiver_features() |>
    plot_model_features() +
    labs(title = 'Average Rating')

averageweight_plot =
    averageweight_fit |>
    extract_vetiver_features() |>
    plot_model_features() +
    labs(title = 'Average Weight')

usersrated_plot =
    usersrated_fit |>
    extract_vetiver_features() |>
    plot_model_features() +
    labs(title = 'Users Rated')

```

::: {.panel-tabset}

### Average Weight

```{r}
#| fig-height: 7
#| results: asis
#| echo: false

averageweight_plot

```

### Average 

```{r}
#| fig-height: 7
#| results: asis
#| echo: false
average_plot

```

### Users Rated

```{r}
#| fig-height: 7
#| results: asis
#| echo: false
usersrated_plot

```

:::
